Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-04-29 paper/Analisis.tex
FEHOMOGENEOUS plot upgrade + a bit more of text
added references and first paragraph in the conclusions

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig} 
\usepackage{float} 
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

\title[Rotation in the Lyman-$\alpha$ line]{Effects of rotation on the
  Lyman-$\alpha$ line morphology in distant galaxies}
\author[N. Garavito and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Nicolas Garavito-Camargo.$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Universidad de los Andes
$^{2}$Uni B
}
\maketitle

@@

In this paper we study for the first time the impact of rotation on
the morphology of the Lyman $\alpha$ line. To isolate the effects of
rotation we focus on a simple system: the gas distribution is
spherical, with homogenous density and the gas rotates as a solid
body.

@@

@@

\subsection{Integrated flux}

@@

\section{Observational implications}
% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.

... The results derived in this paper have consequences on the
interpreation of galaxy observations in the Lyman alpha line.

\section{Conclusions}

@@

@@

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{Cd94} Author, \emph{Title}, Journal/Editor, (year)

%\end{thebibliography}

>>>>

\documentclass[usenatbib]{mn2e} 
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{epsfig} 
\usepackage{float} 
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\bibliographystyle{mn2e}
% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{blue}{rgb}{0.1,0.3,0.9}
\newcommand{\blue}{\color{blue}}

@@

\title[Rotation in the Lyman-$\alpha$ line]{Rotation effects on the
  Lyman-$\alpha$ line morphology in distant galaxies}
\author[N. Garavito and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Nicolas Garavito-Camargo$^{1}$,
  Jaime E. Forero-Romero$^{1}$ 
}
\vspace*{6pt}\\
$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
}
\maketitle

@@

In this paper we study for the first time the impact of rotation on
the morphology of the Lyman $\alpha$ line. To isolate the effects of
rotation we focus on a simple system: the gas distribution is
spherical, with homogenous density and the gas rotates as a solid
body. We base our work on the Monte Carlo base radiative transfer code
CLARA \citep{CLARA}.

@@

Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot)

@@

\subsection{Integrated flux in a narrow band filter}

@@

... Comparison with Verhamme et al. results on the rotation

... The results derived in this paper have consequences on the
interpreation of galaxy observations in the Lyman alpha line.
% taking into account equivalent widths results with narrow band
% filters we can make a criterium in order to select wich galaxie
% could be seen in actual observations.

\section{Conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Lyman$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.

@@

\bibliography{references}

@@
